---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

form_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSAD4pmNsvX_VPGpldfPmP8HhuGrVa0UXMXrAprTFpvUORIEWT-Av9Gwowh7NmXqUrNHK8vREjU9J5M/pub?output=csv"

logged_data <- read_csv(form_url)

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
    location = `Where are you making this observation?`,
    people_count = `How many people are in the study space at the time of observation?`,
    noise_level = `What is the overall noise level?`
  ) %>%
  mutate(
    people_count = as.numeric(people_count),
    noise_level = factor(
      noise_level,
      levels = c("Very quiet", "Mostly quiet", "Moderate", "Noisy", "Very noisy")
    )
  )

report_summary <- latest_data %>%
  summarise(
    total_observations = n(),
    mean_people = round(mean(people_count, na.rm = TRUE), 1),
    max_people = max(people_count, na.rm = TRUE)
  )

location_counts <- latest_data %>%
  count(location, sort = TRUE)

noise_counts <- latest_data %>%
  count(noise_level, sort = TRUE)

top_location <- location_counts %>%
  slice(1) %>%
  pull(location)

top_location_n <- location_counts %>%
  slice(1) %>%
  pull(n)

common_noise <- noise_counts %>%
  slice(1) %>%
  pull(noise_level)

common_noise_n <- noise_counts %>%
  slice(1) %>%
  pull(n)
```

```{css}
body {
  font-family: Arial, sans-serif;
  margin: 20px;
  line-height: 1.6;
}

h2, h3 {
  color: #2c3e50;
}

.dynamic-comment {
  background-color: #eef6ff;
  border-left: 5px solid #5b8def;
  padding: 12px;
  margin-bottom: 16px;
  border-radius: 6px;
}
```

## Study space observations on campus

This dynamic report summarises observational logging data collected from campus study spaces.  
The report focuses on where observations were made, how many people were present, and the overall noise level.

### Dynamic comments

- There are **`r report_summary$total_observations`** observations in this dataset.
- The average number of people observed was **`r report_summary$mean_people`**.
- The highest number observed in a study space was **`r report_summary$max_people`**.
- The most frequently observed study space was **`r top_location`** with **`r top_location_n`** observations.
- The most common noise level was **`r common_noise`** with **`r common_noise_n`** observations.

### Number of observations by study space

```{r}
latest_data %>%
  ggplot(aes(x = location)) +
  geom_bar() +
  labs(
    title = "Number of observations by study space",
    subtitle = "Study space observation log",
    x = "Study space",
    y = "Number of observations"
  ) +
  coord_flip() +
  theme_minimal()
```

### Noise level across observations

```{r}
latest_data %>%
  ggplot(aes(x = noise_level)) +
  geom_bar() +
  labs(
    title = "Noise level across observations",
    subtitle = "Study space observation log",
    x = "Noise level",
    y = "Number of observations"
  ) +
  theme_minimal()
```
